Multisensor Architecture for an Intersection Management System

### 2015-04-08 ch2-mdf_ims.tex
Added fifth and last IMS component paragraph, Implementation Added another conclusion in chapter 2

many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure. For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.

Other application are traffic-control oriented, rather than to sensing and data-processing stage. The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety. Many works have been done and although their objective is the same, are diverse between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).

@@

In \cite{Ball2010} and \cite{Azimi2012}, intervehicular-communication based architectures are proposed. In these, each vehicle send to the others its own information about position, velocity, destination and more, and then they coordinate how the access to the intersection should be done. In \cite{Guerrero-Ibanez2013}, is presented a system capable of work in V2I mode, additional to V2V, using inductive loops and RFID information for detecting vehicles. The information is gathered by an intersection controller which manage the access to the crossroad. Another V2I based systems is presented in \cite{Basma2011}, where wireless magnetic nodes are used to detect presence and to send data to a base station, which determines possible collisions and warns driver through a visualisation system in infrastructure. Furthermore, in \cite{Dresner2008} and \cite{CondeBento2012}, are presented simulation-based systems for traffic controlling, using agents and applied to autonomous vehicles. In \cite{Quinlan2010}, an augmented reality implementation of the system proposed in \cite{Dresner2008} is done. In this work, approaching vehicles request to an intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies.

@@

%\end{document}

>>>>

Not all IMS applications are implementable on a real scenario, maybe because is not the scope of the application or because it is in a early stage and it could be validated in other ways. This types of developments are sometimes implemented and evaluated using simulators, making functional prototypes or deploying scale-models. Some other projects use datasets to evaluate new algorithms and data processing techniques, and then compare obtained results with previous works. Augmented reality is also used as a tool for evaluating and validate developmens, taking advantage of the interaction of a real system with a simulated/artificial scenario.

%many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure. For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.

%Other application are traffic-control oriented, rather than to sensing and data-processing stage. The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety. Many works have been done and although their objective is the same, are diverse between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).

@@

%In \cite{Ball2010} and \cite{Azimi2012}, intervehicular-communication based architectures are proposed. In these, each vehicle send to the others its own information about position, velocity, destination and more, and then they coordinate how the access to the intersection should be done. In \cite{Guerrero-Ibanez2013}, is presented a system capable of work in V2I mode, additional to V2V, using inductive loops and RFID information for detecting vehicles. The information is gathered by an intersection controller which manage the access to the crossroad. Another V2I based systems is presented in \cite{Basma2011}, where wireless magnetic nodes are used to detect presence and to send data to a base station, which determines possible collisions and warns driver through a visualisation system in infrastructure. Furthermore, in \cite{Dresner2008} and \cite{CondeBento2012}, are presented simulation-based systems for traffic controlling, using agents and applied to autonomous vehicles. In \cite{Quinlan2010}, an augmented reality implementation of the system proposed in \cite{Dresner2008} is done. In this work, approaching vehicles request to an intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies.

@@

On the other hand, intersection management systems are highly required to improve safety and mobility in transportation, due to the high complexity present in these places, for drivers and authorities too. There is not an IMS application that address all the needs and problems in an intersection, for this reason many developments with narrow scopes and many topics involved have been proposed through the years. To handle all these works and proposals, a new component-based classification scheme for IMS application has been proposed.
%\end{document}
